---
layout: post
title: "Public Waste Ocurr & Disposal"
author: "Young Ho Lee"
date: "2018.07.21"
categories: Contest
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# basic packages
library(dplyr)
library(stringr)
library(rgdal)
library(classInt)
library(RColorBrewer)
library(reshape2)
library(ggplot2)
library(ggmap)

options(scipen = 10)
```

# 1. Data Import
```{r}
path <- "D:/Data/contest/waste/"

# occurrence
occurrence.houseLife <- read.csv(paste0(path, "2_houseLife.csv"))
occurrence.industrialLife <- read.csv(paste0(path, "2_industrialLife.csv"))
occurrence.life <- read.csv(paste0(path, "2_life.csv"))
occurrence.constructionWaste <- read.csv(paste0(path, "2_construction.csv"))

# disposal
disposal.houseLife <- read.csv(paste0(path, "3_houseLife.csv"))
disposal.industrialLife <- read.csv(paste0(path, "3_industrialLife.csv"))
disposal.industrialWaste <- read.csv(paste0(path, "3_life.csv"))
disposal.constructionWaste <- read.csv(paste0(path, "3_construction.csv"))
# disposal.local <- read.csv(paste0(path, "disposal_local.csv"))

# collect
collect.lifeBusiness <- read.csv(paste0(path, "8_collect_lifeBusiness.csv"))
collect.construction <- read.csv(paste0(path, "8_collect_construction.csv"))

# middle/final/overall
middle.disposal <- read.csv(paste0(path, "8_middle_disposal.csv"))
middle.recycle <- read.csv(paste0(path, "8_middle_recycle.csv"))
middle.construction <- read.csv(paste0(path, "8_middle_construction.csv"))

final.disposal <- read.csv(paste0(path, "8_final_disposal.csv"))
final.recycle <- read.csv(paste0(path, "8_final_recycle.csv"))

overall.recycle <- read.csv(paste0(path, "8_overall_recycle.csv"))
```

# 2. Data Handling
## 1) Layout(Long -> Wide / Occurrence)
```{r}
occurrence.life <- occurrence.life[, -c(3:4, 34)]
occurrence.life[, 19] <- as.numeric(as.character(occurrence.life[, 19]))

# file names
file.names <- c("occurrence.houseLife", "occurrence.industrialLife", 
                "occurrence.life", "occurrence.constructionWaste")

# data handling
for (i in file.names) {
  # data
  tmp <- get(i)
  
  # rename
  names(tmp)[1:3] <- c("sido", "sigungu", "type")
  
  # NA
  for (j in 4:ncol(tmp)) {
    tmp[is.na(tmp[, j]), j] <- 0
  }
  
  # row sum
  tmp$sum <- apply(tmp[, 4:ncol(tmp)], 1, sum)
  
  # feature selection
  tmp <- tmp[, c(1:3, ncol(tmp))]
  
  # cast & variable names
  if (i == "occurrence.life") {
    tmp.df <- tmp %>%
      group_by(sido, sigungu, type) %>%
      summarise(newSum = sum(sum))
    df <- dcast(tmp.df, sido + sigungu ~ type, value.var = "newSum")
    names(df)[3:7] <- paste(substr(i, 12, nchar(i)), 
                            c("landfill", "total", "incin", "recycle", "sea"),
                            sep = ".")
  } else {
    df <- dcast(tmp, sido + sigungu ~ type, value.var = "sum")
    names(df)[3:6] <- paste(substr(i, 12, nchar(i)), 
                            c("landfill", "total", "incin", "recycle"),
                            sep = ".")
  }
  
  # join key
  df$region <- paste(df$sido, df$sigungu, sep = "_")
  
  # assign data
  assign(i, tmp)
  assign(paste0(i, ".df"), df)
}
```

## 2) Merge(Occurrence)
```{r}
occurrence.local <- Reduce(function(x, y) merge(x, y, all = TRUE), 
                           list(occurrence.houseLife.df, 
                                occurrence.industrialLife.df, 
                                occurrence.life.df, 
                                occurrence.constructionWaste.df))

# NA
for (i in 12:16) {
  occurrence.local[is.na(occurrence.local[, i]), i] <- 0
}
```

## 3) Disposal Data
### 1) Feature Extract
```{r}
list.disposal.name <- c("disposal.houseLife",
                        "disposal.industrialLife",
                        "disposal.constructionWaste")

for (i in c(list.disposal.name)) {
  ## (0) bring the data
  i %in% ls(envir = .GlobalEnv)
  data <- get(i, envir = .GlobalEnv)
            
  ## (1) change the column names
  names(data) <- c("sido","sigungu", "self.landfill", "self.incin",
                   "self.recycle", "business.landfill", "business.incin", 
                   "business.recycle", "own.landfill", "own.incin", 
                   "own.recycle")
        
  ## (2) NA -> 0
  data <- data %>%
    mutate_all(funs(replace(., is.na(.), 0)))
                
  ## (3) Combine columns by disposision type
  data <- data %>%
    mutate(landfill = rowSums(select(., contains("landfill"))),
           incin = rowSums(select(., contains("incin"))),
           recycle = rowSums(select(., contains("recycle"))) )%>%
    select(c(sido, sigungu, landfill, incin, recycle))
        
    ## (4) assign the orignal name to data
  colnames(data)[3:5] <- paste(substr(i, 10, nchar(i)), colnames(data)[3:5], 
                               sep = ".")
    
  assign(x = i, value = data)
  print(paste0(i, " done"))
}
```

```{r}
# disposal.local.industrialWaste has 14 columns.
# so manually handling this data only

## (1)change the column names
names(disposal.industrialWaste) <- c("sido", "sigungu","self.landfill",
                                     "self.incin","self.recycle", "self.sea", 
                                     "business.landfill", "business.incin",
                                     "business.recycle", "business.sea", 
                                     "own.landfill", "own.incin", "own.recycle",
                                     "own.sea")

## (2) NA -> 0
disposal.industrialWaste <- disposal.industrialWaste %>%
  mutate_all(funs(replace(., is.na(.), 0)))

## (3) Combine columns by disposision type
disposal.industrialWaste <- disposal.industrialWaste %>%
  mutate(landfill = rowSums(select(., contains("landfill"))),
         incin = rowSums(select(., contains("incin"))),
         recycle = rowSums(select(., contains("recycle"))),
         sea = rowSums(select(., contains("sea"))))%>%
  select(c(sido, sigungu, landfill, incin, recycle, sea))

## (4) make prefix to diviede each data
tmp.name <- colnames(disposal.industrialWaste)[3:6]
colnames(disposal.industrialWaste)[3:6] <- paste("life", tmp.name, sep = ".")
```

### 2) Merge
```{r}
disposal.local <- Reduce(function(x, y) merge(x, y, all = TRUE),
                         list(disposal.houseLife,
                              disposal.industrialLife,
                              disposal.industrialWaste, 
                              disposal.constructionWaste))
```

### 3) Calculation Total
```{r}
disposal.local <- disposal.local %>%
  mutate(houseLife.total = houseLife.landfill + houseLife.incin + 
                           houseLife.recycle,
         industrialLife.total = industrialLife.landfill + industrialLife.incin +
                                industrialLife.recycle, 
         life.total = life.landfill + life.incin + life.recycle + life.sea,
         constructionWaste.total = constructionWaste.landfill + 
                                   constructionWaste.incin +
                                   constructionWaste.recycle,
         region = paste(sido, sigungu, sep = "_"))
```

## 4) Merge(Occurrence & Disposal)
```{r}
occurrence.re <- occurrence.local[, c(1:3, 5, 9, 13, 18)]
names(occurrence.re)[4:7] <- paste("Oc", names(occurrence.re)[4:7], sep = ".")

disposal.re <- disposal.local[, c(1:2, 20, 16:19)]
names(disposal.re)[4:7] <- paste("Di", names(disposal.re)[4:7], sep = ".")

waste.df <- cbind(occurrence.re, disposal.re[, 4:7])

##
options(scipen = 100)

waste.df <- waste.df %>%
  mutate(houseLife = round(Oc.houseLife.total - Di.houseLife.total, 2),
         industrialLife = round(Oc.industrialLife.total - Di.industrialLife.total, 2),
         industrialWaste = round(Oc.life.total - Di.life.total, 2),
         constructionWaste = round(Oc.constructionWaste.total - Di.constructionWaste.total, 2))
```

## 5) Spatial Data
```{r}
# data import
korea.sp <- readOGR("D:/Data/map/shp/nsdi/kostat/sigungu/sigungu.shp",
                    p4s = "+proj=tmerc +lat_0=38 +lon_0=127 +k=1 +x_0=200000 
                    +y_0=500000 +ellps=bessel +units=m +no_defs",
                    encoding = "UTF8")
sido.code <- read.csv("D:/Data/map/shp/nsdi/kostat/sigungu/sido_code.csv")

sido.sp <- readOGR("D:/Data/map/shp/nsdi/kostat/sido/sido.shp",
                   p4s = "+proj=tmerc +lat_0=38 +lon_0=127 +k=1 +x_0=200000 
                    +y_0=500000 +ellps=bessel +units=m +no_defs",
                    encoding = "UTF8")

# coordinate system
wgs <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
korea.wgs <- spTransform(korea.sp, CRS(wgs))
korea.df <- data.frame(korea.wgs)

# merge
korea.re <- korea.df %>%
  mutate(sido.code = substr(SIGUNGU_CD, 1, 2))

korea.re <- merge(korea.re, sido.code, by.x = "sido.code", by.y = "sido_code",
                  all.x = TRUE)
```

## 6) Merge(Spatial Data & Occurrence / Disposal)
```{r}
# dissolve
korea.re$SIGUNGU_NM <- as.character(korea.re$SIGUNGU_NM)
dissolve.lnfo <- nchar(korea.re$SIGUNGU_NM) >= 5
korea.re[dissolve.lnfo, 5] <- substr(korea.re[dissolve.lnfo, 5], 1, 3)

# merge(occurrence)
korea.re <- korea.re %>%
  mutate(region = paste(sido_name, SIGUNGU_NM, sep = "_"))

occurence.wgs <- merge(korea.re[, -c(6:7)], occurence.local[, 3:20], 
                       by = "region", all.x = TRUE)
disposal.wgs <- merge(korea.re[, -c(6:7)], disposal.local[, 3:20], 
                      by = "region", all.x = TRUE)
```

## 7) Arrange
```{r}
id.order1 <- order(occurence.wgs$OBJECTID)
id.order2 <- order(disposal.wgs$OBJECTID)

occurence.wgs <- occurence.wgs[id.order1, ]
disposal.wgs <- disposal.wgs[id.order2, ]
```

## 8) Collect Data
### 1) Feature Selection
```{r}
collect.lifeBusiness <- collect.lifeBusiness[c(1, 2, 4, 6, 7, 9, 10)]
collect.construction <- collect.construction[c(1, 2, 3, 4, 5, 8)]

# rename
colnames(collect.lifeBusiness) <-  c("sido", "sigungu",
                                     "company_name", "company_boss",
                                     "location", "collect_15amount", "type")
colnames(collect.construction) <- c("sido", "sigungu",
                                    "company_name", "company_boss",
                                    "location", "collect_15amount")

# adding type column at collect.construction data 
collect.construction$type <- NULL
collect.construction <- collect.construction %>%
    mutate(type = "건축")
```

## 9) Middle / Final / Overall
### 1) Feature Selection
```{r}
middle.disposal <- middle.disposal[c(1, 2, 3, 4, 6, 7, 9, 10, 11, 12, 13, 14, 
                                     18)] 
middle.recycle <- middle.recycle[c(1, 2, 3, 5, 6, 8, 9, 13)] 
middle.construction <- middle.construction[c(1, 2, 3, 4, 5, 7, 14, 18)]

final.disposal <- final.disposal[c(1, 2, 3, 6, 7, 9, 10, 11, 12, 17)]
final.recycle <- final.recycle[c(1, 2, 3, 5, 6, 8, 9, 13)]

overall.recycle <- overall.recycle[c(1, 2, 3, 5, 6, 8, 9, 13)]
```

### 2) Rename
```{r}
# middle
colnames(middle.disposal) <- c("sido", "sigungu", "category", "company_name", 
                               "company_boss", "location", "ic", "md", "cd", 
                               "bd","etcd", # merge disposal column : done
                               "capacity", "disposal_15amount")
colnames(middle.recycle) <- c("sido", "sigungu",
                              "company_name" ,"company_boss", "location",
                              "category", "capacity", "disposal_15amount")
colnames(middle.construction) <- c("sido", "sigungu",
                                   "company_name", "location", "company_boss",
                                   "lf_area","capacity", "disposal_15amount")

# final
colnames(final.disposal) <- c("sido", "sigungu",
                              "company_name", "company_boss", "location",
                              "disposal_target",
                              "lf_area", "lf_capacity", "lf_cumulate",
                              "disposal_15amount") 
colnames(final.recycle) <- c("sido", "sigungu",
                             "company_name", "company_boss", "location",
                             "category", "capacity", "disposal_15amount") 

# overall
colnames(overall.recycle) <- c("sido", "sigungu",
                              "company_name", "company_boss", "location",
                              "category", "capacity", "disposal_15amount") 
```

### 3) Data Handling
```{r}
# combine disposal columns to one 
## change column class
for (i in c("ic", "md", "cd", "bd", "etcd")) {
  middle.disposal[, i] <- as.character(middle.disposal[, i])
}

## make blank to NA
for (i in names(middle.disposal)[c(7:11)]) {
  if(i == "bd"){
    next()
  } else {
    middle.disposal[middle.disposal[, i] == "", i] <- NA
  }
}

## combine disposal column
middle.disposal$category <- dplyr::coalesce(middle.disposal$ic, 
                                            middle.disposal$md, 
                                            middle.disposal$cd, 
                                            middle.disposal$bd,
                                            middle.disposal$etcd)
## featureSelection
middle.disposal <- middle.disposal %>%
  select(-c(ic, md, cd, bd, etcd))
middle.disposal <- middle.disposal[, c(1, 2, 4:6, 3, 7, 8)]
```

## 10) Integrate : collect.occurrence
```{r}
# delete duplicated row and change type vlaue 
collect.lifeBusiness <- collect.lifeBusiness[!duplicated(collect.lifeBusiness$company_name), ] 
collect.lifeBusiness$type <- as.character(collect.lifeBusiness$type)
collect.lifeBusiness[, "type"] <- "생활/사업/음식"

# rbind
collect.occurrence <- rbind(collect.lifeBusiness, collect.construction)

# Data handling
collect.occurrence <- collect.occurrence %>%
  mutate(collect_15amount = as.numeric(round(collect_15amount, 2))) %>%
  mutate(company = paste0(company_name, "_" ,company_boss)) %>% 
  select(-c(company_name, company_boss)) %>%
  arrange(sido, sigungu, company)

collect.occurrence <- collect.occurrence[c(1, 2, 6, 3, 4, 5)]
```

## 11) Integrate : mfo.disposal
```{r}
# data handling
for (i in c("middle.disposal", "middle.recycle", "middle.construction")) {
  i %in% ls(envir = .GlobalEnv)
  data <- get(i, envir = .GlobalEnv)
  if (i == "middle.construction") {
    data <- data %>%
      mutate(disposal_15amount = as.numeric(gsub(",", "", disposal_15amount)),
             capacity = as.numeric(str_split(capacity, 
                                             pattern = " ")[[1]][1]),
             category = "매립",
             company = paste0(company_name, "_", company_boss))%>%
             select(-c(company_boss, company_name))
  } else {
    data <- data %>%
      mutate(company = paste0(company_name, "_", company_boss),
             disposal_15amount = as.numeric(gsub(",", "",
                                                 disposal_15amount))) %>%
      select(-c(company_boss, company_name))
  }

  # list.wise deletion
  data[is.na(data$disposal_15amount) == TRUE, "disposal_15amount"] <- 0
  data <- data[data$sido != "",]
  assign(x = i, value = data)
}

# reorder and selection the column
middle.construction <- middle.construction[c(1, 2, 3, 7, 5, 6, 8)]
```

```{r}
# merge 3 middle data 
m.disposal <- do.call("rbind", list(middle.disposal, 
                                    middle.recycle, 
                                    middle.construction))
m.disposal <- m.disposal %>%
  arrange(sido, sigungu,company)
```

## 12) Final
```{r}
# final.disposal
final.disposal <- final.disposal %>%
  rename(capacity = lf_capacity) %>%
  mutate(category = "매립",
         company = paste0(company_name, "_", company_boss),
         capacity = as.numeric(gsub(",", "", capacity)),
         disposal_15amount = as.numeric(gsub(",", "", disposal_15amount))) %>%
  select(-c(company_boss, company_name,
         disposal_target, lf_area, lf_cumulate))

final.disposal <- final.disposal[, c("sido", "sigungu", "location",
                                     "category", "capacity",
                                     "disposal_15amount", "company")]

# final.recycle
final.recycle <- final.recycle %>%
  mutate(company = paste0(company_name, "_", company_boss),
         capacity = as.numeric(gsub(",", "", capacity)),
         disposal_15amount = as.numeric(gsub(",", "", disposal_15amount))) %>%
  select(-c(company_boss, company_name))

final.recycle <- final.recycle[, c("sido", "sigungu", "location",
                                   "category", "capacity",
                                   "disposal_15amount", "company")]
```

```{r}
# merge 2 final data 
f.disposal <- do.call("rbind", list(final.disposal, # merge
                                    final.recycle))
f.disposal <- f.disposal[f.disposal$sido != "",] # listwise deletion

f.disposal <- f.disposal %>%
  arrange(sido, sigungu, company) # column arrange 
```

## 13) Overall
```{r}
overall.recycle <- overall.recycle %>%
  mutate(company = paste0(company_name, "_", company_boss),
         capacity = as.numeric(gsub(",",  "", capacity)),
         disposal_15amount = as.numeric(gsub(",", "", disposal_15amount))) %>%
  select(-c(company_boss, company_name)) 

overall.recycle <- overall.recycle[c("sido", "sigungu", "location",
                                     "category", "capacity",
                                     "disposal_15amount", "company")] 


o.disposal <- overall.recycle[overall.recycle$sido != "",] # listwise deletion
```

## 14) Make : mfo.disposal
```{r}
mfo.disposal <- do.call("rbind", list(m.disposal, # merge
                                      f.disposal,
                                      o.disposal))
```

## 15) Address
```{r}
collect.occurrence <- collect.occurrence %>%
  mutate(address = paste(sido, sigungu, location))
mfo.disposal <- mfo.disposal %>%
  mutate(address = paste(sido, sigungu, location))

# write.csv(collect.occurrence, "collect_occurrence.csv", row.names = FALSE)
# write.csv(mfo.disposal, "mfo_disposal.csv", row.names = FALSE)
```

# 3. Visualization
## 1) Collect & Disposal
### 1) Data Import
```{r}
path <- "D:/Data/contest/waste/"

collect.occurrence <- read.csv(paste0(path, "collect_occurrence.csv"))
mfo.disposal <- read.csv(paste0(path, "mfo_disposal.csv"))
geocoding.collect <- read.csv(paste0(path, "geocoding_collect.csv"))
geocoding.disposal <- read.csv(paste0(path, "geocoding_disposal.csv"))
```

### 2) Merge
```{r}
collect.final <- cbind(collect.occurrence, geocoding.collect[, -1])
disposal.final <- cbind(mfo.disposal, geocoding.disposal[, -1])
```

### 3) Spatial Points
```{r}
collect.wgs <- SpatialPoints(collect.final[, 9:10], proj4string = CRS(wgs))
disposal.wgs <- SpatialPoints(disposal.final[, 10:11], proj4string = CRS(wgs))
```

### 4) Merge(for ggmap)
```{r}
collect.m <- collect.final %>%
  select(x, y) %>%
  mutate(type = "collect")

disposal.m <- disposal.final %>%
  select(x, y) %>%
  mutate(type = "disposal")

ggmap.df <- rbind(collect.m, disposal.m)

set.seed(1234)
index <- sample(x = 1:nrow(ggmap.df))
ggmap.df <- ggmap.df[index, ]
```

### 5) Plot(only location)
```{r}
# x, y axis
x <- bbox(korea.wgs)

plot(korea.wgs, border = "Grey 50")
plot(disposal.wgs, pch = 19, cex = 0.8, add = TRUE, col = "indianred")
axis(1, at = seq(x[1], x[3], by = ((x[3] - x[1]) / 4)), 
     labels = parse(text = degreeLabelsEW(seq(x[1], x[3],
                                          by = ((x[3] - x[1]) / 4)))))
axis(2, at = seq(x[2], x[4], by = ((x[4] - x[2]) / 4)), 
     labels = parse(text = degreeLabelsNS(seq(x[2], x[4], 
                                          by = ((x[4] - x[2]) / 4)))))
```

```{r}
plot(korea.wgs, border = "Grey 50")
plot(collect.wgs, pch = 19, cex = 0.8, add = TRUE, col = "skyblue")
axis(1, at = seq(x[1], x[3], by = ((x[3] - x[1]) / 4)), 
     labels = parse(text = degreeLabelsEW(seq(x[1], x[3],
                                          by = ((x[3] - x[1]) / 4)))))
axis(2, at = seq(x[2], x[4], by = ((x[4] - x[2]) / 4)), 
     labels = parse(text = degreeLabelsNS(seq(x[2], x[4], 
                                          by = ((x[4] - x[2]) / 4)))))
```

```{r}
basemap <- get_map(location = "south korea", source = "google", 
                   maptype = "roadmap", zoom = 7)

ggmap(basemap) +
  geom_point(data = ggmap.df, aes(x = x, y = y, alpha = .01,
                                  color = type)) +
  guides(alpha = "none")
```

# <2018.08.06>
## 1) Data Handling
### 1) Collect
```{r}
# 3. Visualization - 2) Collect & Disposal - 1) Data Import / 2) Merge
collect.sigungu <- collect.final %>%
  group_by(sido, sigungu) %>%
  summarise(collect_count = n(), 
            collect_15amount = sum(collect_15amount)) %>%
  mutate(region = paste(sido, sigungu, sep = "_"))
```

### 2) Disposal
```{r}
disposal.sigungu <- disposal.final %>%
  group_by(sido, sigungu) %>%
  summarise(disposal_count = n(), 
            disposal_15amount = sum(disposal_15amount),
            capacity = sum(capacity)) %>%
  mutate(region = paste(sido, sigungu, sep = "_"))
```

### 3) Merge
```{r}
# 2. Data Handling - 5) Spatial Data / 6) Merge(Sptial Data...)
# collect.csv - seoul, junggu / busan, jingu / busan, haeundae
# mfo_disposal.csv - capacity & disposal_15amount : NA -> 0
korea.cd <- merge(korea.re[, -c(3, 6, 7)], collect.sigungu[, -c(1:2)], 
                  by = "region", all.x = TRUE)
korea.cd <- merge(korea.cd, disposal.sigungu[, -c(1:2)], by = "region",
                  all.x = TRUE)
```

### 4) NA
```{r}
korea.cd <- korea.cd %>%
  mutate_all(funs(replace(., is.na(.), 0)))
```

### 5) Arrange
```{r}
id.order <- order(korea.cd$OBJECTID); korea.cd <- korea.cd[id.order, ]
```

### 6) Index
```{r}
korea.cd <- korea.cd %>%
  mutate(index = collect_15amount - disposal_15amount)
```

## 2) Visualization
### 1) Count
```{r}
# Collect
x <- bbox(korea.wgs) # x, y axis
blues <- brewer.pal(5, "Blues") # color
ccount.class <- classIntervals(korea.cd$collect_count, n = 5, 
                               style = "quantile") # class
a1 <- ccount.class[[2]]

plot(korea.wgs, col = findColours(ccount.class, blues), border = FALSE)
axis(1, at = seq(x[1], x[3], by = ((x[3] - x[1]) / 4)), 
     labels = parse(text = degreeLabelsEW(seq(x[1], x[3],
                                          by = ((x[3] - x[1]) / 4)))))
axis(2, at = seq(x[2], x[4], by = ((x[4] - x[2]) / 4)), 
     labels = parse(text = degreeLabelsNS(seq(x[2], x[4], 
                                          by = ((x[4] - x[2]) / 4)))))
legend(130.20, 37.40, fill = blues,
       legend = c(paste("Less than", a1[2]), paste(a1[2], "-", a1[3]), 
                  paste(a1[3], "-", a1[4]), paste(a1[4], "-", a1[5]),
                  paste("More than", a1[5])),
       title = "Collect Count", cex = 1.4, bty = "n")
```

```{r}
# Disposal
x <- bbox(korea.wgs) # x, y axis
reds <- brewer.pal(5, "Reds") # color
dcount.class <- classIntervals(korea.cd$disposal_count, n = 5, 
                               style = "quantile") # class
a2 <- dcount.class[[2]]

plot(korea.wgs, col = findColours(dcount.class, reds), border = FALSE)
axis(1, at = seq(x[1], x[3], by = ((x[3] - x[1]) / 4)), 
     labels = parse(text = degreeLabelsEW(seq(x[1], x[3],
                                          by = ((x[3] - x[1]) / 4)))))
axis(2, at = seq(x[2], x[4], by = ((x[4] - x[2]) / 4)), 
     labels = parse(text = degreeLabelsNS(seq(x[2], x[4], 
                                          by = ((x[4] - x[2]) / 4)))))
legend(130.20, 37.40, fill = reds,
       legend = c(paste("Less than", a2[2]), paste(a2[2], "-", a2[3]), 
                  paste(a2[3], "-", a2[4]), paste(a2[4], "-", a2[5]),
                  paste("More than", a2[5])),
       title = "Disposal Count", cex = 1.4, bty = "n")
```

### 2) Capacity
```{r}
x <- bbox(korea.wgs) # x, y axis
purples <- brewer.pal(5, "Purples") # color
pcount.class <- classIntervals(korea.cd$capacity, n = 5, 
                               style = "quantile") # class
a3 <- pcount.class[[2]]

plot(korea.wgs, col = findColours(pcount.class, purples), border = FALSE)
axis(1, at = seq(x[1], x[3], by = ((x[3] - x[1]) / 4)), 
     labels = parse(text = degreeLabelsEW(seq(x[1], x[3],
                                          by = ((x[3] - x[1]) / 4)))))
axis(2, at = seq(x[2], x[4], by = ((x[4] - x[2]) / 4)), 
     labels = parse(text = degreeLabelsNS(seq(x[2], x[4], 
                                          by = ((x[4] - x[2]) / 4)))))
legend(130.20, 37.40, fill = purples,
       legend = c(paste("Less than", a3[2]), paste(a3[2], "-", a3[3]), 
                  paste(a3[3], "-", a3[4]), paste(a3[4], "-", a3[5]),
                  paste("More than", a3[5])),
       title = "Capacity", cex = 1.4, bty = "n")
```

### 3) Amount
```{r}
x <- bbox(korea.wgs) # x, y axis
ryb <- brewer.pal(9, "RdYlBu") # color
acount.class <- classIntervals(korea.cd$index, n = 9, 
                               style = "quantile") # class
a4 <- round(acount.class[[2]], 2)

plot(korea.wgs, col = findColours(acount.class, ryb), border = FALSE)
axis(1, at = seq(x[1], x[3], by = ((x[3] - x[1]) / 4)), 
     labels = parse(text = degreeLabelsEW(seq(x[1], x[3],
                                          by = ((x[3] - x[1]) / 4)))))
axis(2, at = seq(x[2], x[4], by = ((x[4] - x[2]) / 4)), 
     labels = parse(text = degreeLabelsNS(seq(x[2], x[4], 
                                          by = ((x[4] - x[2]) / 4)))))
legend(130.20, 37.40, fill = ryb,
       legend = c(paste("Less than", a4[2]), paste(a4[2], "-", a4[3]), 
                  paste(a4[3], "-", a4[4]), paste(a4[4], "-", a4[5]),
                  paste(a4[5], "-", a4[6]), paste(a4[6], "-", a4[7]),
                  paste(a4[7], "-", a4[8]), paste(a4[8], "-", a4[9]),
                  paste("More than", a4[9])),
       title = "Collect - Disposal", cex = 1.4, bty = "n")
```

```{r}
x <- bbox(korea.wgs) # x, y axis
blues <- brewer.pal(5, "Blues") # color
cacount.class <- classIntervals(korea.cd$collect_15amount, n = 5, 
                               style = "quantile") # class
a5 <- cacount.class[[2]]

plot(korea.wgs, col = findColours(cacount.class, blues), border = FALSE)
axis(1, at = seq(x[1], x[3], by = ((x[3] - x[1]) / 4)), 
     labels = parse(text = degreeLabelsEW(seq(x[1], x[3],
                                          by = ((x[3] - x[1]) / 4)))))
axis(2, at = seq(x[2], x[4], by = ((x[4] - x[2]) / 4)), 
     labels = parse(text = degreeLabelsNS(seq(x[2], x[4], 
                                          by = ((x[4] - x[2]) / 4)))))
legend(130.20, 37.40, fill = blues,
       legend = c(paste("Less than", a5[2]), paste(a5[2], "-", a5[3]), 
                  paste(a5[3], "-", a5[4]), paste(a5[4], "-", a5[5]),
                  paste("More than", a5[5])),
       title = "Collect Amount", cex = 1.4, bty = "n")
```

```{r}
x <- bbox(korea.wgs) # x, y axis
reds <- brewer.pal(5, "Reds") # color
dacount.class <- classIntervals(korea.cd$disposal_15amount, n = 5, 
                               style = "quantile") # class
a6 <- dacount.class[[2]]

plot(korea.wgs, col = findColours(dacount.class, reds), border = FALSE)
axis(1, at = seq(x[1], x[3], by = ((x[3] - x[1]) / 4)), 
     labels = parse(text = degreeLabelsEW(seq(x[1], x[3],
                                          by = ((x[3] - x[1]) / 4)))))
axis(2, at = seq(x[2], x[4], by = ((x[4] - x[2]) / 4)), 
     labels = parse(text = degreeLabelsNS(seq(x[2], x[4], 
                                          by = ((x[4] - x[2]) / 4)))))
legend(130.20, 37.40, fill = reds,
       legend = c(paste("Less than", a6[2]), paste(a6[2], "-", a6[3]), 
                  paste(a6[3], "-", a6[4]), paste(a6[4], "-", a6[5]),
                  paste("More than", a6[5])),
       title = "Collect Amount", cex = 1.4, bty = "n")
```
